---
title: "Analysis of cars data"
author: "Carlos Andres Pillajo"
date: "11/16/2020"
output:
  slidy_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  ioslides_presentation: default
mode: selfcontained
job: Pitch Presentation
subtitle: Variables and MPG
highlighter: highlight.js
widgets: bootstrap
---

## Coursera Reproducible Pitch

### See the Regression Models Course Project  


- This assignment has two parts the first one is a shiny app that you would find at my github link (bellow), and this second part is a  reproducible pitch presentation made using Slidify about my app that is an analysis of mtcars Data set."

- Shiny online app URL: *https://capillajos.shinyapps.io/CarAnalyzer/*
- github repo URL: *https://github.com/capillajos/DDP_courseproject*

---

### Find all details of the assignment here

URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

---

## mtcars Dataset

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.

```{r}
library(datasets)
head(mtcars, 8)
```
---

## mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

```{r}
library(datasets)
dim(mtcars)
```

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Analysis - Main Code

```r
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)  })
  ...
  output$fit <- renderPrint({
    summary(fit()) })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })  })
```
---

## Last Notes

Thank you! Hope this might help you in starting out down the awesome data science path.



